---
output:
  github_document:
    toc: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
knitr::knit_hooks$set(
  prompt = function(before, options, envir) {
    options(prompt = if (options$engine %in% c("sh", "bash")) "$ " else "R> ")
  }
)
```

```{r pkg_load, warning=FALSE, message=FALSE, echo=FALSE}
require(rportal)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/umccr/rportal/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/umccr/rportal/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

# 🔮 rportal - Interacting with the UMCCR Data Portal

## 🍕 Installation

```r
devtools::install_github("umccr/rportal")
# remotes::install_github("umccr/rportal")
```


## 🌀 CLI

{rportal} currently has one convenience wrapper for generating presigned URLs for
bioinformatics data (FASTQs, BAMs, VCFs and HTMLs/TSVs):

### Bioinformatics Data Sharing

A `datashare.R` command line interface is available for convenience.
You need to export the `rportal/inst/scripts/datashare/` directory to your `PATH` in order to use `datashare.R`:

```{bash eval=FALSE, echo=TRUE}
datashare_cli=$(Rscript -e 'x = system.file("scripts/datashare", package = "rportal"); cat(x, "\n")' | xargs)
export PATH="${datashare_cli}:${PATH}"
```

```{bash prompt=TRUE, echo=FALSE}
datashare_cli=$(Rscript -e 'x = system.file("scripts/datashare", package = "rportal"); cat(x, "\n")' | xargs)
export PATH="${datashare_cli}:${PATH}"

echo "datashare.R --version" & datashare.R --version
echo ""
echo "#-----------------------------------#"
echo "datashare.R --help" & datashare.R --help
echo ""
```

## 🚕 Running

```bash
datashare.R \
  --subject_id SBJ0XXXX \
  --library_id_tumor L230XXXX \
  --wts \
  --csv_output urls_SBJ0XXXX_L230XXXX.csv
```
